---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  eval      = FALSE,
  collapse  = TRUE,
  comment   = "#>",
  fig.path  = "man/figures/README-",
  out.width = "100%"
)
```


[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/UBESP-DCTV/rexams.svg?branch=master)](https://travis-ci.org/UBESP-DCTV/rexams)
[![Coverage status](https://codecov.io/gh/UBESP-DCTV/rexams/branch/master/graph/badge.svg)](https://codecov.io/github/UBESP-DCTV/rexams?branch=master)

# rexams

The goal of rexams is to provide functionalities to automatically check
  and evaluate exams at UBESP.

## Install
To install the development version (the only one for the moment) from
GitHub:

```{r}
# install.packages("devtools")
devtools::install_github("UBESP-DCTV/rexams")
```

Once the package is installed, simply load it
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, eval = FALSE}
library(rexams)
```


## Usage
The package is inteded to provide coding exam templates. Those template are 
fancy-commented standard .R code-files to provide instruction to the students 
about how to complete them. The comment are written in compiant way with knitr
parsing capability to produce a final printable version of the exam. 

The package provide two main function:

  - `check_my_exam()`: return the score that could obtained if the exam was
      submitted at the moment
  - `submit_my_exam()`: conclude the exam, produce the corresponding HTML/PDF,
      and provide the possible final score (to be confirmed by the teacher).

## Feature request
If you need some more features, please open an issue on
[github](https://github.com/UBESP-DCTV/rexams/issues).


## Bug reports
If you encounter a bug, please file a
[reprex](https://github.com/tidyverse/reprex) (minimal reproducible example) on
[github](https://github.com/UBESP-DCTV/rexams/issues).


## Code of conduct
Please note that this project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).

By participating in this project you agree to abide by its terms.
